% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font(download helvetica.sty)
%\usepackage{newcent} % uses new century schoolbook postscript font

\begin{document}

\name{Zo\"{e} E. Gagnon}
% \address used twice to have two lines of address
\address{720-301-4407 / zoe@zgagnon.com}
\address{Twitter: @ZoeCraftsCode}

\begin{resume}
 
\section{EXPERIENCE}
{\sl Software Engineering Manager, Pivotal Labs} \hfill December 2017 - Current\\
\begin{itemize}
\item Coached two software engineers in advancing their careers.
\item Worked to advance agile and engineering practices both within and without the company.
\item Developed innovative practices for cloud and micro-services based, React front end applications.
\end{itemize}

{\sl Senior Software Engineer, Pivotal Labs} \hfill October 2015 - November
2017\\
Pivotal, New York
\begin{itemize}
\item Lead balanced product development teams and multi-team efforts to deliver high impact software for 
Fortune 100 clients.
\item Enabled developers and stakeholders in evidence-driven, value-first agile software development.
\item Designed and implemented sustainable cloud based applications and platforms.


\end{itemize}
{\sl Services Engineer} \hfill November 2014 - August 2015\\
Tumblr, New York NY
\begin{itemize}
\item Contributed to ongoing development of Colossus, a
high-performance Scala micro-services
framework.
\item Created a proxy server designed to run in Amazon EC2 cloud
services which reduced S3 transfers and lowered monthly transfer
costs by one sixth.
\item Developed a solution for real-time updates using the
Tumblr firehose, generating over 1 million Redis increments a
second.
\end{itemize}

{\sl Scala Developer} \hfill October 2013 - November 2014\\
Placeable, Denver CO
\begin{itemize} 
\item Created a system for generic data manipulation and export
in a Play 2.2 based service, with distribution to services such
as Google, Yelp, and Factual.
\item Developed and implemented a migration path from multiple
Play instances to a clustered Akka actor system, using Mongo
capped collections as an event bus.
\item Wrote documentation of API for internal and external use
in preparation for enabling third-party applications.
\end{itemize}

{\sl Software Engineer} \hfill Aug 2011 - Aug 2013 \\
     ClickFox, Denver CO
\begin{itemize}
 % \itemsep -2pt % reduce space between items\item Developed and maintained industry-leading cross-channel
%business analysis tools in Java using distributed GreenPlum
%databases and GridGain compute grids.
\item Drove adoption of modern tools and practices, including
best practices of Mercurial source control and Maven build tool,
and integration of Jenkins build server with Redmine issue
tracking.
\item Championed usage of agile methodologies; intrudoced a
two-week sprint and test driven development.
\end{itemize}
 \pagebreak
 
{\sl Java Engineer} \hfill          Aug 2010- May 2011 \\
                Innoprise Software, Broomfield CO
\begin{itemize} 
% \itemsep -2pt %reduce space between items
\item Lead developer on a time-card entry system presented in
the Eclipse Rich Application Platform, hosted using GlassFish
OSGI, to integrate with the Innoprise enterprise resource
planning tools.
\end{itemize} 	 
	    
{\sl Lead Software Quality Assurance / Software Developer}
\hfill Mar 2009 - Aug 2011 \\
Regis Learning Solutions, Inc (now The Regis Company), Golden CO\begin{itemize} 
% \itemsep -2pt %reduce space between items
\item Developed and implemented test plans for e-learning
software. Testing involved creating test scripts on GUI
intensive applications, and exploratory testing in identified
problem areas.
\item Added Section 508 Accessibility compliance to a SCORM
framework in ActionScript 3.
\item Created tools to quickly visualize XML configuration files
using Java 6.
    \end{itemize} 

\section{EDUCATION} {\sl Bachelor of Science,} Computer Science
\\
% \sl will be bold italic in New Century Schoolbook (or	        % any postscript font) and just slanted in
		% Computer Modern (default) font
Metropolitan State University of Denver, Denver CO, 2010 \\               Minor: Mathematics

\section{PUBLIC APPEARANCES}
\begin{itemize}
\item Global Diversity CFP Day - Workshop Facilitator, Jan 2018
\item Spring One Conference - Solid In The Wild, Dec 2017
\item Write Speak Code - Workshop facilitator, Nov 2017
\item Pivotal Tech Talk Tuesdays - Introduction to Reactive Streams, Jun 2017
\item She Says Horror Stories 2 - Panelist, Oct 2016
\item CODE Debugging the Gender Gap Screening - Panelist, May 2016
\end{itemize}

\section{TEXT MEDIA}
\begin{itemize}
\item Being Your Authentic Self - Interview, Built To Adapt
\item Asking for Gender in Applications - Article, Built To Adapt
\end{itemize}

\section{GROUPS AND ACTIVITIES}        
\begin{itemize}   %\itemsep -2pt %reduce space between items
\item Write/Speak/Code - New York Meetup Co-Organizer, Conference Talk Selection Committee
\item Global Diversity CFP Day - New York Co-Organizer, Workshop Facilitator
\item Codebar.io - Coach
\item Interests: Clothing design, French cooking and baking.
\end{itemize}
 

\end{resume}
\end{document}







